Data Specialization for a Staged Lambda Calculus

### 2015-02-17 paper/example.tex
finished a pass through 3.0-3.1
really simple pure2grnd pass

@@

Ignoring for the moment all \texttt{pure} annotations, the first-stage code in
\texttt{qsStaged} looks like \texttt{qSelect}: in the first stage, terms of
non-circle type are available for immediate use. Indeed, we case on the list as
usual, and in the \texttt{Cons} branch, \texttt{part}ition it.

@@

Our type system, discussed in \ref{sec:semantics}, ensures that the staging
annotations are consistent, in the sense that computations marked as
first-stage cannot depend on ones marked as second-stage. The $\curr$ and
\texttt{pure} annotations further distinguish those first-stage computations
which do not contain any embedded second-stage code. (Code \emph{inside}
\texttt{pure}, like the \texttt{part}ition function, is guaranteed not to
contain second-stage code; other code, like \texttt{qsStaged}, may.) We will
discuss the importance of this additional distinction in \ref{sec:splitting}.

>>>>

\crem{Now that hold is not officially in the language, I think we have to put a
function prototype in the quickselect code figure. (And move the footnote about
it to the end of 3.1.}

@@

Ignoring for the moment all \texttt{grnd} annotations, the first-stage code in
\texttt{qsStaged} looks like \texttt{qSelect}: in the first stage, terms of
non-circle type are available for immediate use. Indeed, we case on the list as
usual, and in the \texttt{Cons} branch, \texttt{part}ition it.

@@

Our type system, discussed in \ref{sec:semantics}, ensures that the staging
annotations are consistent, in the sense that computations marked as
first-stage cannot depend on ones marked as second-stage. The $\curr$ and
\texttt{grnd} annotations further distinguish those first-stage computations
which do not contain any embedded second-stage code. (Code \emph{inside}
\texttt{grnd}, like the \texttt{part}ition function, is guaranteed not to
contain second-stage code; other code, like \texttt{qsStaged}, may.) We will
discuss the importance of this additional distinction in \ref{sec:splitting}.

### 2015-02-17 paper/semantics.tex
really simple pure2grnd pass

We express two-stage programs as terms in \lang, a typed, modal lambda calculus
with products, sums, and isorecursive types. Its type system has three distinct
\emph{worlds} \bbonep, \bbonem, and \bbtwo, which respectively classify
\emph{purely first-stage} computations (\bbonep); 
first-stage computations containing a \emph{mix} of code from each stage
(\bbonem); 
and second-stage computations (\bbtwo).

>>>>

We express two-stage programs as terms in \lang, a typed, modal lambda calculus
with products, sums, and isorecursive types. Its type system has three distinct
\emph{worlds} \bbonep, \bbonem, and \bbtwo, which respectively classify
\emph{ground first-stage} computations (\bbonep); 
first-stage computations containing a \emph{mix} of code from each stage
(\bbonem); 
and second-stage computations (\bbtwo).
